Operational Feature Selection with Gaussian Mixture Models for remote sensing images

### 2016-10-07 paper.tex
improve indent
Petite modif

        \begin{prop}[Decision function~\ref{eq:decision}]
            \begin{align}
            \label{eq:q-update}
                Q(\mathbf{x}) = &- \underbrace{(\mathbf{x}^{(k-1)} - \boldsymbol{\mu}^{(k-1)})^t (\boldsymbol{\Sigma}^{(k-1)})^{-1} (\mathbf{x}^{(k-1)} - \boldsymbol{\mu}^{(k-1)})}_{\substack{\text{computed once}\\ \text{per selection step}}} \nonumber \\
                &- \underbrace{\log \left(|\boldsymbol{\Sigma}^{(k-1)}|\right) + 2 \log (\pi_c) + k \log(2 \pi)}_{\substack{\text{computed once}\\ \text{per selection step}}} \nonumber \\
                &- \underbrace{\alpha \left( \left[\begin{array}{cc} \mathbf{v}^t & \frac{1}{\alpha} \end{array}\right] (\mathbf{x}^{(k)} - \boldsymbol{\mu}^{(k)}) \right)^2 - \log \alpha}_{\substack{\text{computed for} \\ \text{each augmented set}}}.
            \end{align}
        \end{prop}

@@

    \begin{minted}[fontsize=\tiny,bgcolor=bg]{sh}
otbcli_TrainGMMSelectionApp -io.il hyper.tif \
			    -io.vd reference.shp \
			    -gmm.varnb 20 -gmm.method forward -gmm.crit jm\
			    -gmm.best 1 -gmm.seed 0\
			    -io.out model.txt

otbcli_PredictGMMApp -in hyper.tif \
		     -model model.txt -modeltype selection\
		     -out ThematicMap.tif
    \end{minted}
    \caption{OTB Module: The feature selection is done on the image \emph{hyper.tif} using the training set from \emph{reference.shp}. The feature selection algorithm is the forward search used with the Jeffries-Matusita criterion, 20 features are extracted and the corresponding GMM model is saved in \emph{model.txt}. Then the whole image is classified using the model and the results is saved in the geotiff \emph{ThematicMap.tif}.}
    \label{fig:otb:ffs}
  \end{figure}
\section{Data-sets}
\label{sec:datasets}
Numerical experiments  have been conducted on  two different data-sets.
The first  dataset, called  \emph{Aisa}, is an  airborne hyperspectral
dataset  and  the  second,  called \emph{Potsdam},  is  an  very  high
resolution multispectral airborne image.

>>>>

        \begin{prop}[Decision function~\ref{eq:decision}]
            \begin{align}
            \label{eq:q-update}
                Q(\mathbf{x}) = &- \underbrace{(\mathbf{x}^{(k-1)} - \boldsymbol{\mu}^{(k-1)})^t (\boldsymbol{\Sigma}^{(k-1)})^{-1} (\mathbf{x}^{(k-1)} - \boldsymbol{\mu}^{(k-1)})}_{\substack{\text{computed once per selection step}}} \nonumber \\
                &- \underbrace{\log \left(|\boldsymbol{\Sigma}^{(k-1)}|\right) + 2 \log (\pi_c) + k \log(2 \pi)}_{\substack{\text{computed once per selection step}}} \nonumber \\
                &- \underbrace{\alpha \left( \left[\begin{array}{cc} \mathbf{v}^t & \frac{1}{\alpha} \end{array}\right] (\mathbf{x}^{(k)} - \boldsymbol{\mu}^{(k)}) \right)^2 - \log \alpha}_{\substack{\text{computed for each augmented set}}}.
            \end{align}
        \end{prop}

@@

    \begin{minted}[fontsize=\scriptsize,bgcolor=bg]{sh}
otbcli_TrainGMMSelectionApp -io.il hyper.tif \
			    -io.vd reference.shp \
			    -gmm.varnb 20 \
                            -gmm.method forward \
                            -gmm.crit jm \
			    -gmm.best 1 -gmm.seed 0 \
			    -io.out model.txt

otbcli_PredictGMMApp -in hyper.tif \
                     -model model.txt \
                     -modeltype selection \
		     -out ThematicMap.tif
    \end{minted}
    \caption{OTB Module: The feature selection is done on the image \emph{hyper.tif} using the training set from \emph{reference.shp}. The feature selection algorithm is the forward search used with the Jeffries-Matusita criterion, 20 features are extracted and the corresponding GMM model is saved in \emph{model.txt}. Then the whole image is classified using the model and the results is saved in the geotiff \emph{ThematicMap.tif}.}
    \label{fig:otb:ffs}
  \end{figure}
\section{Data-sets}
\label{sec:datasets}
Numerical experiments  have been conducted on  two different data-sets.
The first  dataset, called  \emph{Aisa}, is an  airborne hyperspectral
dataset  and  the  second,  called \emph{Potsdam},  is  an  very  high
resolution multispectral airborne image.
